Misspecification Demonstration

### 2022-07-12 misspecification_study/misspec_demo.Rmd

>>>>

The catch and index four panel plots all look good for UR_em4.

![catch 4 panel](UR_em4/plots_png/diagnostics/Catch_4panel_fleet_1.png)

![index 1 4 panel](UR_em4/plots_png/diagnostics/Index_4panel_1.png)

![index 2 4 panel](UR_em4/plots_png/diagnostics/Index_4panel_2.png)

The problematic diagnostic is the NAA 4 panel plots, show below for ages 1 and 8 as well as the stacked barplot of residuals.

![NAA age 1 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_1.png)
![NAA age 8 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_8.png)
![NAA residuals stacked barplot](UR_em4/plots_png/diagnostics/NAA_res_barplot_stacked.png)
